Future cosmic microwave background delensing with galaxy surveys

### 2018-04-13 Notes/galaxy_delensing.tex
adding 3G MSIP

DES is modeled after the DES Science Verification public data release.
For DESI we used the $\frac{dN}{dz}$ in Tab. 2.3 of \cite{Aghamousa:2016zmz}. From that we can derive the galaxy density of 0.63 galaxies per squared arcmin.

@@

\refeq{Bres} highlights the different factors that control the delensing efficiency.
The first part of the second term in the parenthesis consists of an inverse variance filter applied to the measured E-mode.
The smaller the noise in the E-modes ($N^{EE}$) is the closer this term is to a value of one: a less noisy measurement improves the template of the lensing B-modes.
The second captures the difference between the reconstructed $\phi$ and the CMB lensing potential, and it directly relates the residual power after delensing with the cross-correlation coefficients with CMB lensing of the tracers used.
The larger the $\rho_{\ell}^{2}$ is for an LSS field, the more it is correlated with the lensing potential acting on the CMB photons. A higher correlation allows for a better reconstruction of $\phi$ and, as a consequence, of $B^{\rm{lens}}$ leading to a smaller residual power $C_{{l}}^{BB,\mathrm{res}}$.
We conclude this section showing in \reffig{bbplot} the expected residual lensing B-modes power spectrum for some of the tracers used in this work together with the primordial B-modes component and the instrumental noise for current and future experiments.

>>>>

DES is modeled after the DES Science Verification public data release.
For DESI we used the $\frac{dN}{dz}$ in Tab. 2.3 of \cite{desi-collaboration:2016}. From that we can derive the galaxy density of 0.63 galaxies per squared arcmin.

@@

\refeq{Bres} highlights the different factors that control the delensing efficiency.
The first part of the second term in the parenthesis consists of an inverse variance filter applied to the measured E-mode.
The smaller the noise in the E-modes ($N^{EE}$) is the closer this term is to a value of 1: a less noisy measurement improves the template of the lensing B-modes.
The second captures the difference between the reconstructed $\phi$ and the CMB lensing potential, and it directly relates the residual power after delensing with the cross-correlation coefficients with CMB lensing of the tracers used.
The larger the $\rho_{\ell}^{2}$ is for an LSS field, the more it is correlated with the lensing potential acting on the CMB photons. A higher correlation allows for a better reconstruction of $\phi$ and, as a consequence, of $B^{\rm{lens}}$ leading to a smaller residual power $C_{{l}}^{BB,\mathrm{res}}$.
We conclude this section showing in \reffig{bbplot} the expected residual lensing B-modes power spectrum for some of the tracers used in this work together with the primordial B-modes component and the instrumental noise for current and future experiments.
